Bayesian Sparsification of Deep $\cplx$-valued networks

### 2020-01-31 paper/paper.tex
removed citations from the abstract, added its condensed version into intro, fixed the title

\title{Bayesian Sparsification of $\cplx$-valued networks}
\author{Ivan Nazarov, and Evgeny Burnaev}

@@

\begin{abstract}
With continual miniaturization ever more applications of deep learning can be found in
embedded systems, where it is common to encounter data with natural complex domain
representation. To this end we extend Variational Dropout of \citet{kingma_variational_2015}
and \citet{kharitonov_variational_2018} to complex-valued neural networks building upon
the work of \citet{trabelsi_deep_2017}. We verify the proposed Bayesian technique and
assess the performance-compression trade-off by conducting a large-scale numerical study
of $\cplx$-valued networks on two tasks: image recognition on MNIST-like and CIFAR10
datasets and music transcription on MusicNet. We reliably replicate the state-of-the-art
result by \citet{thickstun_learning_2017} for $\cplx$-valued networks on MusicNet with
$50-100\times$ compression rate.
\end{abstract}

@@

% our contribution
Inspired by variational sparsification and stochastic sparsification techniques we
develop bayesian dropout for $\cplx$-valued networks.
%
The paper is structured as follows. In sec.~\ref{sec:bayesian_dropout} we review Bayesian
dropout techniques, and in sec.~\ref{sec:c_valued_networks} we provide a brief summary of
the inner working of complex-valued networks as functions of complex argument. The main
contribution of this study is presented in sec.~\ref{sec:dropout_for_c_valued_layers},
where we consider different variational approximations and priors, outline the tricks
and derive expressions for the divergence term. In sec.~\ref{sec:experiments} we evaluate
the sparsification rate and compare the resulting performance of various $\cplx$-networks
proposed in prior work, and discuss the outcomes.

>>>>

\title{Bayesian Sparsification of Deep $\cplx$-valued networks}
\author{Ivan Nazarov, and Evgeny Burnaev}

@@

\begin{abstract}
With continual miniaturization ever more applications of deep learning can be found
in embedded systems, where it is common to encounter data with natural complex domain
representation. To this end we extend Variational Dropout to complex-valued neural
networks. We verify the proposed Bayesian technique and assess the performance-compression
trade-off by conducting a large-scale numerical study of $\cplx$-valued networks on
two tasks: image recognition on MNIST-like and CIFAR10 datasets and music transcription
on MusicNet. We reliably replicate the state-of-the-art result by \citet{trabelsi_deep_2017}
for $\cplx$-valued networks on MusicNet with $50-100\times$ compression rate.
\end{abstract}

@@

% our contribution
Inspired by variational sparsification and stochastic sparsification techniques we
extend Bayesian dropout for $\cplx$-valued networks. We assess the performance-compression
trade-off of the the proposed Bayesian technique by conducting a large-scale numerical
study of $\cplx$-valued networks on two tasks: image recognition on MNIST-like and CIFAR10
datasets and music transcription on MusicNet, \citep{thickstun_learning_2017}. We reproduce
the state-of-the-art result by \citet{trabelsi_deep_2017} for $\cplx$-valued networks on
the latter with $\approx 1-2\%$ of remaining non-zero parameters.

The paper is structured as follows. In sec.~\ref{sec:bayesian_dropout} we review Bayesian
dropout techniques, and in sec.~\ref{sec:c_valued_networks} we provide a brief summary of
the inner working of complex-valued networks as functions of complex argument. The main
contribution of this study is presented in sec.~\ref{sec:dropout_for_c_valued_layers},
where we consider different variational approximations and priors, outline the tricks
and derive expressions for the divergence term. In sec.~\ref{sec:experiments} we evaluate
the sparsification rate and compare the resulting performance of various $\cplx$-networks
proposed in prior work, and discuss the outcomes.
